Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-26 paper.tex
update

uncomputable solutions

A naive solution to is to use precise call stack modeling as we did in concrete
CESK machine. Instead of allocating continuations on store and recording an 
address of continuations, we

@@

@@

TODO: summarize CFA2, PDCFA, AAC, P4F

On the other side, \citeauthor{darais2017abstracting} construct abstracting 
definitional interpreters (ADI) that automatically inherit the pushdown control-flow 
property from the defining language. TODO

In the rest of this section, we take a closer look at the two state-of-art techniques
to accomplish perfect call-stack precision.

>>>>

A naive solution to is to use precise call stack modeling as we did in concrete
CESK machine. Instead of allocating continuations on store and recording an 
address of continuations, we leave the call stack unabstracted.

@@

Unfortunately, even though other components is finite, this AAM with unbounded stack is uncomputable. 
Because the unbounded stack can grow to arbitrary deep and this implies that the state space is possibly 
infinite, therefore the analysis may not terminate for all programs if we simply enumerating 
reachable states.
To see this, consider a program that has two mutually recursived functions:

\begin{verbatim}
(letrec ([f1 (lambda (x) 
               (let ([x1 (f2 x)]) x1))]
         [f2 (lambda (y)
               (let ([y1 (f1 y)]) y1))])
  (let ([z (f1 1)])
    z))
\end{verbatim}

\texttt{f1} and \texttt{f2} call each others, and the stack will be interleaved
pushing \texttt{f1} and \texttt{f2} onto the top of current stack, but not existing 
two stack components are the same in the state space.

@@

CFA2 is the first solution that solves the return-flows problem\cite{vardoulakis2010cfa2}.
But CFA2 has several drawbacks: it works only on continuation-passing style programs, 
and only allows monovariant analysis, in addition with an exponential time complexity.
TODO: summarize PDCFA, AAC, P4F

On the other side, with the insight from Reynold that the defined language will inherit properties
from the defining language, \citeauthor{darais2017abstracting} construct abstracting 
definitional interpreters (ADI) that automatically inherit the pushdown control-flow 
property from the defining language.
TODO: connection to this paper.

Question: although they establish pushdown control-flow analysis in different ways, 
is there a correspondence between different methods?

In the rest of this section, we take a closer look at the P4F and ADI which are
two state-of-art techniques to accomplish perfect call-stack precision.
